Pool Model - A Mathematical Framework for Modelling Bacterial Consortia in Food Science

### 2025-12-11 paper/pool_model.tex
Christian's changes to maxwell stress section

    \dot{\gamma} = \Gamma f\left(\dot{T}\right)-\delta \gamma.
The dimensionless function $f$, with $f(0)=0$ and $f: \mathbb{R}\to\mathbb{R}_{\ge 0}$, evaluates the effect of a temperature change, i.e., a change from $T=2$ to $T=12$ could have a different effect as a change from $T=14$ to $T=4$. $\Gamma$ is a scaling factor and $\delta$ is the relaxation time for the temperature disturbance.

@@

    \gamma(t) = \Gamma \int_0^t f\left(\dot{T}(t^{\prime})\right)e^{-\delta (t-t^{\prime})}dt^{\prime}.

@@

    \gamma(t) = \Gamma\alpha\left [T(t)-T(0)e^{-\delta t}-\delta

@@

    \gamma(t) = \Gamma(1-\alpha)\left [T(0)e^{-\delta t}-T(t)+\delta

@@

    \gamma(t) &=& \Gamma\sum_{i=1}^n f\left(\Delta T_i \right)\theta(t-t_i)e^{-\delta(t-t_i)}.

@@

        The parameters of the back-flow rate are $\Gamma=1^\circ C / s$ and $\delta=5~\mathrm{s}^{-1}$.

>>>>

    \dot{\gamma} = \sigma f\left(\zeta\dot{T}\right)-\delta \gamma.
The dimensionless function $f$, with $f(0)=0$ and $f: \mathbb{R}\to\mathbb{R}_{\ge 0}$, evaluates the effect of a temperature change, i.e., a change from $T=2$ to $T=12$ could have a different effect as a change from $T=14$ to $T=4$. $\zeta$ is a scaling factor, $\sigma$ is a kind of stiffness telling how strongly the bacteria react to temperature stress, and $\delta^{-1}$ is the relaxation time for the temperature disturbance.

@@

    \gamma(t) = \sigma\int_0^t f\left(\zeta\dot{T}(t^{\prime})\right)e^{-\delta (t-t^{\prime})}dt^{\prime}.

@@

    \gamma(t) = \sigma\alpha\zeta\left [T(t)-T(0)e^{-\delta t}-\delta

@@

    \gamma(t) = \sigma(1-\alpha)\zeta\left [T(0)e^{-\delta t}-T(t)+\delta

@@

    \gamma(t) &=& \sigma\sum_{i=1}^n f\left(\zeta\Delta T_i \right)\theta(t-t_i)e^{-\delta(t-t_i)}.

@@

        The parameters of the back-flow rate are $\zeta=1 s/K $ and $\delta=5~\mathrm{s}^{-1}$.
